Systematic studies of correlations between different order flow harmonics in $\PbPb$ collisions at $\snn = 2.76$~TeV

### 2017-05-08 appendix.tex
6.2

% !TEX root = paper.tex
\appendix
\section{Model comparison of the Individual flow harmonics $v_n$}
As discussed in Sec~\ref{sec:method}, NSC$(m,n)$ is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$ but SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual $v_{n}$ harmonics. Therefore it is important to check how well the individual flow harmonics $v_n$ are tuned in the models.

@@

The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia} in Fig.~\ref{fig:Figure_8}, where the initial conditions and $\eta/s$ parameterizations are chosen to reproduce the LHC $v_n$ data.
The calculations captures the centrality dependence of the individual $v_2$ , $v_3$ , and $v_4$ harmonics in the central and midcentral collisions with a precision better than 5\% for $v_2$ and 10\% for $v_3$ and $v_4$.

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/vishcom_v2.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/vishcom_v3.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/vishcom_v4.eps}}
        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}. Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors and markers. The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.}
        \label{fig:Figure_9}
              \end{center}
\end{figure*}

The VISH2+1 calculations with various initial conditions and $\eta/s$ parameters are compared to the individual flow harmonics $v_n$ (n=2, 3 and 4) in Fig.~\ref{fig:Figure_9}.
Neither MC-Glauber nor MC-KLN initial conditions can simultaneously describe $v_2$ , $v_3$ and $v_4$. More specifically, for MC-Glauber initial conditions, VISH2+1 with $\eta/s$ = 0.08 could nicely fit $v_2$ from central to midcentral collisions, but overestimates $v_3$ and $v_4$ for the same centrality ranges. For MC-KLN initial conditions, VISH2+1 with $\eta/s$ = 0.20 reproduces $v_2$ but underestimates $v_3$ and $v_4$ for the presented centrality regions. Compared with these two calculations, hydrodynamic calculations with AMPT initial conditions improves the descriptions of $v_n$ (n = 2, 3, 4). Overall difference to the data is less than 30\% for $v_2$ and $v_3$,  50\% for $v_4$.

@@

The individual flow harmonics $v_n$ (n=2, 3 and 4) are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_10}.
The string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces $v_n$ (n=2, 3 and 4) as shown in Fig.~\ref{fig:Figure_10} with a precision better than 5\%. The version based on the string melting configuration without the hadronic rescattering phase underestimates the data quite a bit, which demonstrates that large fraction of the flow is developed during the hadronic rescattering stage in the string melting version of AMPT.
However the default version of AMPT underestimates $v_n$ (n=2, 3 and 4) by almost 20\%. It should be noted that the default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.

@@

Finally, only the best calculations from three models are compared to the data in Fig.~\ref{fig:Figure_11}.
The calculations from the event-by-event EKRT+viscous hydrodynamic, VISH2+1 with AMPT initial conditions and the string melting version of AMPT give the best description of the individual flow harmonics $v_n$ (n=2, 3 and 4) with a precision of 5-20\% in general and the centrality dependence is different for there models in different order harmonic flows.
The simultaneous description of all order flow harmonics is necessary to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions together with SC$(m,n)$ and NSC$(m,n)$.

>>>>

% !TEX root = paper.tex
\appendix
\section{Model comparisons of the Individual flow harmonics $v_n$}
As discussed in Sec~\ref{sec:method}, NSC$(m,n)$ is expected to be insensitive to the magnitudes of $v_{m}$ and $v_{n}$ but SC$(m,n)$ has contributions from both the correlations between the two different flow harmonics and the individual $v_{n}$ harmonics. Therefore it is important to check how well the individual flow harmonics $v_n$ are produced in the theoretical models used in Sec~\ref{sec:theory}.

@@

The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV are compared to the event-by-event EKRT+viscous hydrodynamic calculations~\cite{Niemi:2015qia} in Fig.~\ref{fig:Figure_8}, where the initial conditions and $\eta/s$ parameterizations are chosen to reproduce the LHC $v_n$ data.
The calculations captures the centrality dependence of $v_n$ in the central and midcentral collisions with a precision better than 5\% for $v_2$ and 10\% for $v_3$ and $v_4$.

\begin{figure*}[h]
            \begin{center}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/vishcom_v2.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/vishcom_v3.eps}}
                       \resizebox{0.31\textwidth}{!}{\includegraphics{figs/vishcom_v4.eps}}
        \caption{The individual flow harmonics $v_n$ (n=2, 3 and 4) in $\PbPb$ collisions at $\snn=2.76$~TeV~\cite{Adam:2016izf} are compared to various VISH2+1 calculations~\cite{Zhu:2016puf}. Three initial conditions from AMPT, MC-KLN and MC-Glauber are drawn as different colors. The $\eta/s$ parameters are shown as different line styles, the small shear viscosity ($\eta/s=0.08$) are shown as solid lines, and large shear viscosities ($\eta/s=0.2$ for MC-KLN and MC-Glauber, 0.16 for AMPT) are drawn as dashed lines.}
        \label{fig:Figure_9}
              \end{center}
\end{figure*}

The VISH2+1 calculations with various initial conditions and $\eta/s$ parameters are compared to $v_n$ data in Fig.~\ref{fig:Figure_9}.
Neither MC-Glauber nor MC-KLN initial conditions can simultaneously describe $v_2$, $v_3$ and $v_4$. More specifically, for MC-Glauber initial conditions, VISH2+1 with $\eta/s$ = 0.08 could nicely fit $v_2$ from central to midcentral collisions, but overestimates $v_3$ and $v_4$ for the same centrality ranges. For MC-KLN initial conditions, VISH2+1 with $\eta/s$ = 0.20 reproduces $v_2$ but underestimates $v_3$ and $v_4$ for the presented centrality regions. Compared with these two calculations, hydrodynamic calculations with AMPT initial conditions improves the descriptions of $v_n$ (n = 2, 3, 4). Overall difference to the data is quite large if all the model settings are considered, about 30\% for $v_2$ and $v_3$,  50\% for $v_4$. The calculations with AMPT initial conditions describe the data better with the precision 10-20\%

@@

The individual flow harmonics $v_n$ (n=2, 3 and 4) are compared to the {AMPT} simulations in Fig.~\ref{fig:Figure_10}.
The string melting version of AMPT~\cite{Lin:2001zk,Lin:2004en} reasonably reproduces $v_n$ as shown in Fig.~\ref{fig:Figure_10} with a precision about 10-20\% for $v_2$ and 10\% for $v_3$ and $v_4$. The version based on the string melting configuration without the hadronic rescattering phase underestimates the data quite a bit, which demonstrates that a large fraction of the flow is developed during the late hadronic rescattering stage in the string melting version of AMPT.
However the default version of AMPT underestimates $v_n$ by $\approx$ 20\%. It should be noted that the default AMPT model can describe the normalized symmetric cumulants (NSC($m$,$n$)) quantitively for most centralities while the string melting AMPT model fails to describe them.

@@

Finally, only the best calculations from three models are compared to the $v_n$ data in Fig.~\ref{fig:Figure_11}.
The calculations from the event-by-event EKRT+viscous hydrodynamic, VISH2+1 with AMPT initial conditions ($\eta/s$ =0.08) and the string melting version of AMPT give the best description of the individual flow harmonics $v_n$ (n=2, 3 and 4) with a precision of 5-20\% in general and the centrality dependence differs in three models as well as in different order harmonic flows.
The simultaneous description of all order individual flow harmonics $v_n$ is necessary to further optimize model parameters and put better constraints on the initial conditions and the transport properties of nuclear matter in ultra-relativistic heavy-ion collisions together with SC$(m,n)$ and NSC$(m,n)$.
